---
title: "Using hexwall for Hexagonal Image Tiles"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using hexwall for Hexagonal Image Tiles}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(htmltools)
library(hexwall)
```

## Introduction

The `hexwall` package provides an easy way to create hexagonal tile patterns for displaying images using CSS transforms and htmltools. This is particularly useful for showcasing package logos, project thumbnails, or any collection of square/hexagonal images.

## Basic Usage

The main function is `hextile()`, which takes a vector of image paths and creates a hexagonal tiling pattern:

```{r basic-usage}
# Sample image paths (you would replace these with your actual image paths)
sample_images <- c(
  "path/to/image1.svg",
  "path/to/image2.svg", 
  "path/to/image3.svg",
  "path/to/image4.svg",
  "path/to/image5.svg"
)

# Create basic hex tile
hex_display <- hextile(sample_images)
```

## Adding Custom CSS Classes

You can add additional CSS classes for custom styling:

```{r custom-classes}
# Add custom classes
custom_hex <- hextile(sample_images, class = c("my-theme", "large-tiles"))
```

## HTML Output

The function generates clean HTML structure that matches the expected format:

```html
<div class="hextile clr">
  <ul>
    <li><img src="image1.svg"></li>
    <li><img src="image2.svg"></li>
    <li><img src="image3.svg"></li>
    <!-- ... more items ... -->
  </ul>
</div>
```

## CSS Dependency

The package automatically includes the hex.css dependency, which provides:

- Hexagonal shape transforms using CSS `rotate()` and `skew()`
- Responsive tiling layout that adjusts to different screen sizes
- Proper positioning for creating the honeycomb pattern

## Integration with R Markdown and Quarto

The hexwall output integrates seamlessly with R Markdown and Quarto documents:

````
```{r, results='asis'}
my_hex_display <- hextile(c("logo1.png", "logo2.png", "logo3.png"))
my_hex_display
```
````

## Tips for Best Results

1. **Image Format**: SVG images work best as they scale cleanly at any size
2. **Aspect Ratio**: Square or hexagonal images look best in the hex tiles
3. **File Paths**: Use relative paths for portability across different environments
4. **Number of Images**: The layout works well with any number of images, automatically flowing to new rows

## Example with Real Images

Here's a complete example using actual package hex stickers:

```{r real-example, eval=FALSE}
library(htmltools)
library(hexwall)

# URLs to R package hex stickers
hex_stickers <- c(
  "https://raw.githubusercontent.com/rstudio/hex-stickers/master/SVG/dplyr.svg",
  "https://raw.githubusercontent.com/rstudio/hex-stickers/master/SVG/ggplot2.svg",
  "https://raw.githubusercontent.com/rstudio/hex-stickers/master/SVG/readr.svg",
  "https://raw.githubusercontent.com/rstudio/hex-stickers/master/SVG/purrr.svg",
  "https://raw.githubusercontent.com/rstudio/hex-stickers/master/SVG/tibble.svg",
  "https://raw.githubusercontent.com/rstudio/hex-stickers/master/SVG/tidyr.svg"
)

# Create and display the hex wall
tidyverse_hex <- hextile(hex_stickers)
browsable(tidyverse_hex)
```

This creates a beautiful hexagonal display of the tidyverse package logos!